Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-19 paper/main.tex
section 'related work'

@@

% FIXME: na wypadek zmiany tytulu w przyszlsoci!!!!!!!!!! ;-)
This paper\footnote{the original title for this paper was ``Lord Vorotron:
Finding the Best JFA Variant for the Coming Winter''} studies a practical usage of machine learning to automate research
towards discovering efficient Distance Transform algorithms (utilizing technique known as AutoML).
Thus, by finding mutations which works best for specific data, and then ensembling them into
one, we create new state-of-the-art algorithm in this field named \uline{\ourjfa
\hspace{0.01cm} with best-case $O(1)$ time complexity and $O(N)$ work complexity.}
In addition, we introduce \uline{\ourjfasingle, a single
variant that in most cases outperforms original JFA with proven worst-case
$O(\log^{*}N)$ time complexity.}

@@

\begin{enumerate}
	\item Presenting new envolved state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: % \newline
		\textbf{\ourjfasingle} - (Multi-domain) single variant, replacement of JFA;
		\textbf{\ourjfa} - (Ensemble of Domain-specific) multiple weak variants, production ready; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method in different domains.
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

\hl{czy (Ensemble of Domain-specific) weak variants - jest prawidlowo?}

@@

@@

\subsection{Multi-domain Algorithm (\ourjfasingle)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Domain-specific Algorithms} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Ensemble Across Domains (\ourjfa)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%       tak wyglada mieszkanko jak pisze prace w nocy!
%       https://www.youtube.com/watch?v=-5EQIiabJvk

@@

This paper\footnote{the original title for this paper was ``Lord Vorotron:
Finding the Best JFA Variant for the Coming Winter''} studies a practical usage
of machine learning to automate research towards discovering efficient Distance
Transform algorithms (utilizing technique known as AutoML).  Thus, by finding
mutations which works best for specific data, and then ensembling them into one,
we create new state-of-the-art algorithm in this field named \uline{\ourjfa
\hspace{0.01cm} with best-case $O(1)$ time complexity and $O(N)$ work
complexity.} In addition, we introduce \uline{\ourjfasingle, a single variant
that in most cases outperforms original JFA with proven worst-case
$O(\log^{*}N)$ time complexity.}\footnote{source code is available at
\url{https://github.com/maciejczyzewski/fast_gpu_voronoi}}

@@

\begin{enumerate}
	\item Presenting new envolved state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: % \newline
		\textbf{\ourjfasingle} - Multi-domain single variant, replacement of JFA;
		\textbf{\ourjfa} - Ensemble of domain-specific variants, production ready; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method in different domains.
\end{enumerate}

@@

The original author of JFA\footnote{Guodong Rong} defined some variants and
modifications \citep{rong2007variants}, in this work we continue on this subject
and examine the relationship between them.

@@

\subsection{Multi-domain Variant (\ourjfasingle)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Domain-specific Variants} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Ensemble of Domain-specific (\ourjfa)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
